### 2013-07-30 abstract.tex
8 hours qq
Almost done.

This paper considers left/right action-preserving morphisms between Bott-Samelson bimodules from a combinatorial perspective; specifically, using a diagrammatic representation.  We examine the maps formed by a basis known as Libedinsky's light leaves, which constructs a map based on a string $\underline r$, composed of the letters $s$ and $t$, and a binary string $\underline b$.  The eventual goal is to find a formula for the composition of two such maps based on their binary strings $\underline b$.  The paper provides a complete formula for the case $\underline r = sss\dots$, and shows that the possible structures of maps when $\underline r = ststs\dots$ are extremely limited.  We additionally provide a formula for the number of maps between two arbitrary Bott-Samelson bimodules.

>>>>

This paper considers left/right action-preserving morphisms between Bott-Samelson bimodules from a combinatorial perspective; specifically, using a diagrammatic representation.  We examine the maps formed by a basis known as Libedinsky's light leaves, which constructs a map based on a string $\underline r$, composed of the letters $s$ and $t$, and a binary string $\underline b$.  The eventual goal is to find a formula for the composition of two such maps based on the two original binary strings.  The paper provides a complete formula for the case $\underline r = sss\dots$, and shows that the possible structures of maps when $\underline r = ststs\dots$ are, in a certain sense, limited.  We additionally provide a formula for the number of maps between two arbitrary Bott-Samelson bimodules.

### 2013-07-30 appa.tex
Almost done.

\begin{figure}[ht]
	\centering
	\begin{asy}
	size(6cm);
	real xmax=7;
	real ymax=5;
	draw( (xmax,ymax)--(xmax,-ymax)--(-xmax,-ymax)--(-xmax,ymax)--cycle );
	pair apex = (0,2);
	path arc = (5,-5)..(2,0)..apex..(-2,0)..(-5,-5);
	draw(arc, blue);
	dot(apex, blue);
	draw(apex--(0,ymax), blue);
	draw(-apex--(0,-ymax), red + dashed + 0.6);
	dot(-apex, red);
	label("$s$", (0,ymax), dir(90));
	label("$t$", (0,-ymax), dir(270));
	label("$s$", (-5,-ymax), dir(270));
	label("$s$", (5,-ymax), dir(270));
	\end{asy}
	\caption{An example of a possible diagram.}
	\label{fig:example_diagram}
\end{figure}

@@

\setcounter{op}{-1}
\begin{op}[Isotropy] If two diagrams can be continuously deformed into each other (in the topological sense), then they are equivalent.  In other words, the maps are isotropy invariant  \end{op}
The reasons for the above operation are not obvious; see page 7 of \cite{ref:gr4all} for an explanation.
\begin{op}[Associativity] We have $\barbell{assoc_horiz} = \barbell{assoc_vert}$.  \end{op}
\begin{op}[Contraction] We have $\barbell{contract_left} = \barbell{contract_right} = \barbell{alpha_blue}$.  \end{op}
\begin{op}[The Needle] We have $\barbell{needle} = 0$.  \end{op}
\begin{remark*} Using contraction and the above, one can show that the diagram $\barbell{zero}$ is zero as well. In fact, in general, \emph{any} map which contains a ``closed'' and empty region is the zero map.  \end{remark*}
\begin{op}[Barbell-Forcing Rules]
	We have the following three equalities:
	\begin{enumerate}[(a)]
		\ii $\barbell{barbell_blue}\barbell{alpha_blue} + \barbell{alpha_blue} \barbell{barbell_blue} = 2 \barbell{break_blue}$, and the similar equation for red.
		\ii $\barbell{alpha_red}\barbell{barbell_blue} = -x\barbell{break_red} + \barbell{barbell_blue}\barbell{alpha_red} + x \barbell{barbell_red}\barbell{alpha_red}$.
		\ii $\barbell{alpha_blue}\barbell{barbell_red} = -y\barbell{break_blue} + \barbell{barbell_red}\barbell{alpha_blue} + y \barbell{barbell_blue}\barbell{alpha_blue}$.
	\end{enumerate}
\end{op}

>>>>

\begin{figure}[ht]
	\centering
	\begin{asy}
	size(6cm);
	real xmax=7;
	real ymax=5;
	draw( (xmax,ymax)--(xmax,-ymax)--(-xmax,-ymax)--(-xmax,ymax)--cycle );
	pair apex = (0,2);
	path arc = (5,-5)..(2,0)..apex..(-2,0)..(-5,-5);
	draw(arc, s);
	dot(apex, dot_s);
	draw(apex--(0,ymax), s);
	draw(-apex--(0,-ymax), t);
	dot(-apex, dot_t);
	label("$s$", (0,ymax), dir(90));
	label("$t$", (0,-ymax), dir(270));
	label("$s$", (-5,-ymax), dir(270));
	label("$s$", (5,-ymax), dir(270));
	\end{asy}
	\caption{An example of a possible diagram.}
	\label{fig:example_diagram}
\end{figure}

@@

\setcounter{op}{-1}
\begin{op}[Isotropy] If two diagrams can be continuously deformed into each other (in the topological sense), then they are equivalent.  In other words, the maps are isotropy invariant  \end{op}
\begin{remark*}
	The justification for the above operation is not obvious; see page 7 of \cite{ref:gr4all} for an explanation.
\end{remark*}
\begin{op}[Associativity] We have $\barbell{assoc_horiz} = \barbell{assoc_vert}$.  \end{op}
\begin{op}[Contraction] We have $\barbell{contract_left} = \barbell{contract_right} = \barbell{alpha_blue}$.  \end{op}
\begin{op}[The Needle] We have $\barbell{needle} = 0$.  \end{op}
\begin{remark*} Using contraction and the above, one can show that the diagram $\barbell{zero}$ is zero as well. In fact, in general, \emph{any} map which contains a ``closed'' and empty region is the zero map.  \end{remark*}
\begin{op}[Barbell-Forcing Rules]
	We have the following three equalities:
	\begin{enumerate}[(a)]
		\ii $\barbell{barbell_blue}\barbell{alpha_blue} + \barbell{alpha_blue} \barbell{barbell_blue} = 2 \barbell{break_blue}$, and the similar equation for red.
		\ii $\barbell{alpha_red}\barbell{barbell_blue} = -x\barbell{break_red} + \barbell{barbell_blue}\barbell{alpha_red} + x \barbell{barbell_red}\barbell{alpha_red}$.
		\ii $\barbell{alpha_blue}\barbell{barbell_red} = -y\barbell{break_blue} + \barbell{barbell_red}\barbell{alpha_blue} + y \barbell{barbell_blue}\barbell{alpha_blue}$.
	\end{enumerate}
\end{op}

### 2013-07-30 paper.tex
Almost done.

This paper investigates some of the properties of these diagrammatics from a combinatorial perspective.   In this paper, we consider only the special case where the underlying group $W$ of the Hecke algebra is an infinite dihedral group with generators $s$ and $t$ (as opposed to an arbitrary Coxeter group $W$).

@@

Appendix~\ref{sec:prelim_background} contains the preliminaries for the problem; it describes the light leaves and defines the relation between diagrams and maps.  A minimal set of definitions used in this paper is given in Section~\ref{sec:prelim}.  
In Section~\ref{sec:probstate}, the problem statement is given in its full technicality.

The results begin by solving the special case of one color completely in Section~\ref{sec:res_onecolor}.  In Section~\ref{sec:res_count_maps}, we also present a formula for the number of maps between two given bimodules.  The most important results of this paper are presented in Sections~\ref{sec:res_alt_restrict} and \ref{sec:res_alt_compute}, where we investigate a special ``alternating'' case.  In particular, we show that the possible resulting structures are extremely limited, and provide a recursion based on these restrictions for that case.

>>>>

This paper investigates some of the properties of these diagrammatics from a combinatorial perspective.   We consider only the special case where the underlying group $W$ of the Hecke algebra is an infinite dihedral group with generators $s$ and $t$ (as opposed to an arbitrary Coxeter group $W$).

@@

Appendix~\ref{sec:prelim_background} contains the preliminaries for the problem; it describes the light leaves and defines the relation between diagrams and maps.  A minimal set of definitions used in this paper is given in Section~\ref{sec:prelim}.  
In Section~\ref{sec:probstate}, we give the problem statement in its full technicality.

The results begin by solving the special case of one color completely in Section~\ref{sec:res_onecolor}.  In Section~\ref{sec:res_count_maps}, we also present a formula for the number of maps between two given bimodules.  The most important results of this paper are presented in Sections~\ref{sec:res_alt_restrict} and \ref{sec:res_alt_compute}, where we investigate a special ``alternating'' case.  We show that the possible resulting structures are extremely limited in a certain sense.  We then exploit these restrictions to provide a partial recursion to compute the compositions of light leaves in the alternating case.
